Full 18s Community composition

### 2019-10-31 code/whole_18s_community_compare.Rmd
split up wrangle tasks into scripts, made seperate csvs

ggplot(p, aes(x=sample_id %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=phylum), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  facet_grid(~phylum %>% fct_relevel(phylum_ord), switch = "x") +
  labs(title = "Relative abundance plot of 18S phyla", x="Sample ID (from lowest to highest elevation)") +
  cust_theme
```

>>>>

ggplot(p, aes(x=sample_id %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=phylum), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  facet_grid(~phylum %>% fct_relevel(phylum_ord), switch = "x") +
  labs(title = "Relative abundance plot of 18S phyla (SILVA assignments)", x="Sample ID (from lowest to highest elevation)") +
  cust_theme
```
